\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\harpvec{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Calculus III - Spring 2015 - Mr. Clontz - Final Exam
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill\space
  Class:\enspace\hrulefill\space
}

\vspace{12pt}

\begin{itemize}
  \item This exam is open-``everything'', provided you do not plagiarize.
  \item Write your solutions so that a fellow student who has a perfect
        understanding of previous math classes and packets but
        has never seen that type of problem before could follow your work.
  \item You will have 150 minutes to complete this test
        on your own. You may not communicate with anyone during this period.
        Violations will be referred to the university academic honesty
        committee and recommended for expulsion.
\end{itemize}

\newpage

\begin{questions}

\setcounter{question}{0}

\question[10] %r(t)=\<2t+1,e^t-3, \ln t\>
  Find \(\vect{r}(t)\) given
  \(\vect{r}'(t) = \left\<2, e^t, \frac{1}{t}\right\>\)
  and \(\vect{r}(1) = \<3, e-3, 0\>\).

\newpage

\question[10]
  Find the rate of change of $f(x,y,z)=x+2yz^2$ in the direction
  $\vect{u}=\<\frac{1}{3},\frac{2}{3},-\frac{2}{3}\>$
  at the point $P_0=(-3,0,1)$.

\newpage

\question[10]
  Prove that $f(x,y)=x^2-2xy-2x+2y-y^2$ has exactly one critical point,
  and that it yields a saddle point.

\newpage

\question[10]
  Rewrite the Type II integral
  \[
    \int_0^3\int_y^3 \ln(1+x^2) \,dx\,dy
  \]
  as a Type I integral by switching the order of integration.
  (You do not need to evaluate this integral.)

\newpage

\question[10]
  Use the transformation \(\vect{r}(u,v)=\<3+u-v,2+2u+3v\>\) from the unit
  square in the \(uv\) plane to the parallelogram \(R\) with vertices
  \((3,2),(4,4),(3,7),(2,5)\) in the \(xy\) plane to change
  \[
    \iint_R y-2x \,dA
  \]
  to an integral of the varibles \(u\) and \(v\). (You do not need to
  evaluate this integral.)

\newpage

\question[10]% f= xy^2-2x^2y+3y
  Prove that
    \[
      \int_C \<y^2-4xy,2xy-2x^2+3\>\cdot\,d\vect{r}
        =
      -6
    \]
  where \(C\) is the portion of the parabola \(y=x^2+x\) beginning
  at the point \((1,2)\) and ending at the point
  \((-1,0)\). (Hint: this \textit{is} a conservative field.)

\newpage

\question[10]
  Plot the curve $x=z^3$ in the $xz$-plane and the
  cylindrical surface $x=z^3$ in $xyz$-space.

\newpage

\question[10]
  Verify the Mixed Derivative Theorem (\(f_{xy}=f_{yx}\)) for
  $f(x,y)=\sin(x+2y)$.

\newpage

\question[10]
  Find the work done by a force vector field $\<x+y,4x-y-2\>$ moving an
  object around the
  boundary of the triangle with vertices $(0,0)$, $(2,0)$, and
  $(2,4)$ oriented counter-clockwise.

\newpage


\question[10]
  Circle exactly one of the following questions, and then answer it.
  \begin{itemize}
    \item Write a sentence explaining intuitively what the curvature of
    \(\vect{r}(t)=\<t,1-t,2t+5\>\) should be for any point
    on it, and then use a definition or formula
    from our notes to verify your intuition.

    \item The coordinate product of a point \((x,y,z)\) is given by \(xyz\).
    Find the point on the triangle with vertices
    \((6,0,0),(0,6,0),(0,0,6)\) which has the largest coordinate product.
  \end{itemize}

\newpage

\textit{(scratch paper)}

\newpage

\textit{(scratch paper)}

\end{questions}

\end{document}