\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\harpvec{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Calculus III - Spring 2015 - Mr. Clontz - Test 2
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill\space
  Class:\enspace\hrulefill\space
  Type:\enspace\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item This exam is open-``everything'', provided you do not plagiarize.
        \textit{Do not leave any unsupported answers!}
  \item Write your solutions so that a fellow student who has a perfect
        understanding of previous math classes and packets but
        has never seen that type of problem before could follow your work.
  \item Individual Test: You will have 40 minutes to complete this test
        on your own. You may not communicate with anyone during this period.
  \item Group Test: You will have 40 minutes to complete an identical test.
        You may collaborate with your group members during this time. All
        solutions must still be written by yourself, and may not be directly
        copied from another student.
\end{itemize}

\newpage

\begin{questions}

\setcounter{question}{0}

\question[6]
  Prove that the helix given by the vector equation
  $\vect{r}(t) = \<\cos(2t),3t,-\sin(2t)\>$
  has constant curvature $\kappa=\frac{4}{13}$.

\newpage

\question[6]
  Prove that the limit
  \[
    \lim_{(x,y)\to(0,2)}
    \frac{y\cos(3x)-y}{xy^2}
      =
    0
  \]

\newpage

\question[6]
  Find the rate of change of $f(x,y,z)=y^2z-3xz^2$ in the direction
  $\vect{u}=\<\frac{2}{7},-\frac{6}{7},\frac{3}{7}\>$
  at the point $P_0=(0,-2,2)$.

\newpage

\question[6]
  Prove that $f(x,y)=x^3+y^3-3xy-2$ has two critical points, one of
  which yields a local minimum, and another which is a saddle point.

\newpage

\question[6]
  Choose functions $f(x,y)$ and $g(x,y)$ which could be used with the method
  of Lagrange Multipliers to find the point
  on the circle with center $(0,0)$ and radius $10$
  furthest away from the point $(-3,-4)$.
  Be sure to clearly \textbf{explain} how you chose $f$ and $g$,
  but do not actually solve the problem.\footnote{The point on the circle
  furthest away is $(6,8)$ for what it's worth.}


\end{questions}

\end{document}