\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\harpvec{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Calculus III - Spring 2015 - Mr. Clontz - Test 4 Makeup
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill\space
  Class:\enspace\hrulefill\space
  Type:\enspace\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item This exam is open-``everything'', provided you do not plagiarize.
        \textit{Do not leave any unsupported answers!}
  \item Write your solutions so that a fellow student who has a perfect
        understanding of previous math classes and packets but
        has never seen that type of problem before could follow your work.
  \item Individual Test: You will have 40 minutes to complete this test
        on your own. You may not communicate with anyone during this period.
  \item Group Test: You will have 40 minutes to complete an identical test.
        You may collaborate with your group members during this time. All
        solutions must still be written by yourself, and may not be directly
        copied from another student.
\end{itemize}

\newpage

\begin{questions}

\setcounter{question}{0}

\question[8]
  Prove that \[\int_C xy\,d{s}=\int_0^{2\pi} 8\sin t\cos t\,d{t}\]
  where \(C\) is the full counter-clockwise rotation of the circle
  \(x^2+y^2=4\).

\newpage

\question[7]
  Prove that
    \[
      \int_C \<yz,-x,x+y\>\cdot\,d\vect{r}
        =
      % \int_0^{1} \<2t(1-2t),t-1,2-3t\>\cdot\<-1,2,-2\> \,dt
      %   =
      \int_0^1 4t^2+6t-6\,dt
    \]
  where \(C\) is the line segment from \((1,0,1)\) to \((0,2,-1)\).
  (Hint: this is \textit{not} a conservative field.)

\newpage

\question[8] % f=2x+3xyz
  Prove that
    \[
      \int_C \<2+3yz,3xz,3xy\>\cdot\,d\vect{r}
        =
      2
    \]
  where \(C\) is a curve beginning at \((1,2,0)\) and ending at
  \((2,0,-1)\). (Hint: this \textit{is} a conservative field.)

\newpage

\question[7]
  Let \(D\) be the solid bounded by the a surface \(S\).
  Use the Divergence Theorem (section 16.9) to prove that
    \[
      \iint_S \<x^2+1,y^2-xz,1+z^2\>\cdot\,d\vect{\sigma}
        =
      2\iiint_D x+y+z\,dV
    \]



\end{questions}

\end{document}