\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\harpvec{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Calculus III - Spring 2015 - Mr. Clontz - Test 3
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill\space
  Class:\enspace\hrulefill\space
  Type:\enspace\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item This exam is open-``everything'', provided you do not plagiarize.
        \textit{Do not leave any unsupported answers!}
  \item Write your solutions so that a fellow student who has a perfect
        understanding of previous math classes and packets but
        has never seen that type of problem before could follow your work.
  \item Individual Test: You will have 40 minutes to complete this test
        on your own. You may not communicate with anyone during this period.
  \item Group Test: You will have 40 minutes to complete an identical test.
        You may collaborate with your group members during this time. All
        solutions must still be written by yourself, and may not be directly
        copied from another student.
\end{itemize}

\newpage

\begin{questions}

\setcounter{question}{0}

\question[5]
  Divide \(R : 0\leq x\leq 6, -2\leq y\leq 2 \)
  into four congruent pieces arranged two-by-two,
  and then use the midpoint rule to give an arithmetic expression
  approximating the double integral
  \(\ds\iint_R 2xy^2 \,dA\). (You do not need to simplify the arithmetic.)

\newpage

\question[5]
  Evaluate
  \(\ds\iint_R 2xy^2 \,dA\)
  for \(R : 0\leq x\leq 6, -2\leq y\leq 2 \).

\newpage

\question[5]
  Rewrite the Type II integral
  \[
    \int_0^8\int_{x^{1/3}}^2 \frac{1}{1+y^2} \,dy\,dx
  \]
  as a Type I integral by switching the order of integration.
  (You do not need to evaluate this integral.)

\newpage

\question[5]
  Express the average value of the function \(f(x,y,z)=xy^2-z\)
  over the solid cube given by \(0\leq x\leq 4\), \(-1\leq y\leq 2\),
  and \(1\leq z\leq 2\) as a quotient involving one or more triple integrals.
  (You do not need to evaluate any integrals.)

\newpage

\question[5]
  Use the transformation \(\vect{r}(u,v)=\<u+v,1-u+3v\>\) from the unit
  square in the \(uv\) plane to the parallelogram \(R\) with vertices
  \((0,1),(1,0),(2,3),(1,4)\) in the \(xy\) plane to change
  \[
    \iint_R x+y \,dA
  \]
  to an integral of the varibles \(u\) and \(v\). (You do not need to
  evaluate this integral.)

\newpage

\question[5]
  Describe the geometric property that
  \[
    \int_0^{2\pi}\int_0^2\int_0^{\sqrt{4-r^2}}r\,dzdrd\theta
  \]
  represents. Be as specific as possible.
  (You shouldn't have to evaluate the integral to answer this question.)


\end{questions}

\end{document}